### 2017-09-09 paper/evaluation.tex
Added our url and removed a useless sentence

\begin{figure}[t!]
  \centering
  \includegraphics[width=.48\textwidth]{results/testcost-distribution.pdf}
  \caption{\label{fig:time-distributions}Time distributions per projects.}%
\end{figure}
\begin{figure}[t!]
  \centering
  \begin{subfigure}{0.15\textwidth}
    \centering
    \includegraphics[width=.85\textwidth]{results/boxplots-testcases.pdf}
    \caption{\label{fig:size-testsuites}Size of test suites.}
  \end{subfigure}
  ~
  \begin{subfigure}{0.3\textwidth}
    \centering
    \includegraphics[width=.95\textwidth]{results/scatter-testcost.pdf}
    \caption{\label{fig:scattercost}Size versus running time of
      test suites.}
  \end{subfigure}
  \caption{\label{fig:time-versus-size}Relating size and time.
  }%
\end{figure}
Figure~\ref{fig:time-distributions} shows that the average median
times are similar for \medg{} and \longg{}-running test suites.
The difference in overall running times is mainly justified by the
number of test cases as opposed to the individual costs of test cases.
Figure~\ref{fig:size-testsuites} shows the difference in the
distribution of test suite sizes across groups.  This figure indicates
that long projects, albeit having a wider inter-quartile range (middle
50\% projects in this group are less predictable), have a higher
median and much higher average number of test cases.  Furthermore, we
noted a strong positive correlation between running time and number of
test on projects in the \longg{} group.  Considering the \medg{}
group, the correlation between these two variables was weak.
Figure~\ref{fig:scattercost} illustrates this regression line.

>>>>

\begin{figure}[t!]
  \centering
  \includegraphics[width=.48\textwidth]{results/testcost-distribution.pdf}
  \caption{\label{fig:time-distributions}Time distributions per projects.}%
\end{figure}
\begin{figure}[t!]
  \centering
  \begin{subfigure}{0.15\textwidth}
    \centering
    \includegraphics[width=.85\textwidth]{results/boxplots-testcases.pdf}
    \caption{\label{fig:size-testsuites}Size of test suites.}
  \end{subfigure}
  ~
  \begin{subfigure}{0.3\textwidth}
    \centering
    \includegraphics[width=.95\textwidth]{results/scatter-testcost.pdf}
    \caption{\label{fig:scattercost}Size versus running time of
      test suites.}
  \end{subfigure}
  \caption{\label{fig:time-versus-size}Relating size and time.
  }%
\end{figure}
Figure~\ref{fig:time-distributions} shows that the average median
times are similar for \medg{} and \longg{}-running test suites.
The difference in overall running times is mainly justified by the
number of test cases as opposed to the individual costs of test cases.
Figure~\ref{fig:size-testsuites} shows the difference in the
distribution of test suite sizes across groups.  This figure indicates
that long projects, have a higher median and much higher average
number of test cases.
Furthermore, we noted a strong positive correlation between running
time and number of test on projects in the \longg{} group.
Considering the \medg{} group, the correlation between these two
variables was weak.
Figure~\ref{fig:scattercost} illustrates this regression line.
